Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-06 paper/ijcai/paper.tex
pass on Section 3 (up to 3.1)

\subsection{Critical Slicing}
\label{sec:slicing}

@@

\subsection{Spectrum-based Fault Localization}
\label{sec:sfl}

Spectrum-based fault localization (\sfl) is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in
fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
  component can be any code artifact of arbitrary granularity
  such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an
$N\times{}M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.  The pair
$(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{2}{0.3\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

\section{The \sfl{}+Critical Slicing combination}
\label{sec:combination}

The \sfl{}+\cs{} combination consists of four steps:
\begin{enumerate}
  \itemsep0em 
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
  \item Select top $k$ most suspicious source files, according to $R$;
  \item\label{step:compute-slice} Compute slices for every $k$;
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the results obtained in Step~\ref{step:compute-slice} and recompute ranking;
\end{enumerate}

\Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
  falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
  de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
  loop aninhado ao loop ``for every k'' que o lithium-slicer
  implementa (algo como ``for every k and every failing test'')?  Caso
  vc. faca slice contra um teste particular, vc. garante (checa saida)
  que os demais testes que originalmente falhavam continuam falhando
  pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
  de inicio.}

To illustrate the \sfl{}+\cs{} combination, consider a debugging
scenario with five components $c_{1..5}$ and five transactions
$t_{1..5}$, two of which are failing. Consider additionally that the
component $c_2$ is faulty.  Figure~\ref{fig:illustration} shows, at
the left-hand side of the arrow ($\Rightarrow$), the spectra for this
scenario and its corresponding ranking, produced with the Ochiai
predictor. Each line in the ranking shows the ranking position, the
label of the component, and the Ochiai score (in parentheses). The
spectra and ranking appearing at the right-side of the arrow are
obtained with the \sfl{}+\cs{} combination, assuming that the slice
for the transaction $t_2$ is $\{c_2, c_5\}$.  Intuitively, slicing
enables identification of cells in the spectra whose values can be set
to zero, \ie{}, the components marked with 0 are irrelevant to
determine the test output. Let us now observe the impact of this
change at the ranking. Analyzing the Ochiai formula, one can observe
that, for the components $j$ which are not part of the slice of a
failing test, the combination reduces the value of $\N{11}$ and
increases the value of $\N{01}$. Therefore, suspiciosness of those
components decrease. Similar argument applies to other fault
predictors. In the example from Figure~\ref{fig:illustration},
components $c_3$ and $c_4$, which are not in the slice of $t_2$, have
their suspiciousness reduced, enabling the faulty component $c_2$ to
rise from the third to the first position in the ranking.

@@

\Mar{.....parei aqui}

@@

It is possible that a slice that discards the faulty statement still
produces the expected message checked by the oracle. This can happen,
for example, if the oracle is too general.

\vspace{3mm}
\begin{myframe} \label{box:1}
\textbf{java.lang.NullPointerException}, \\
at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
...
\end{myframe}

@@

Section~\ref{sec:oracleheuristics} explains the heuristics
we used to infer oracles for critical slicing that mitigates this
issue.

>>>>

\subsection{Critical Slicing (\cs{})}
\label{sec:slicing}

@@

\subsection{Spectrum-based Fault Localization (\sfl)}
\label{sec:sfl}

Spectrum-based fault localization is a statistical fault
localization technique that takes as input a test suite including at
least one failing test and reports on output a ranked list of
components likely to be in
fault~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}. The
following are given in \sfl{}: a finite set $\mathcal{C}=\set{c_1,c_2,...,c_M}$ of $M$ system \emph{components}\footnote{A
  component can be any code artifact of arbitrary granularity
  such as a class, a method, or a statement~\cite{DBLP:journals/stvr/HarroldRSWY00}.}; a finite set
$\mathcal{T} = \set{t_1,t_2,...,t_N}$ of $N$ system transactions,
which correspond to records of a system execution, such as test cases;
the error vector $e = \set{e_1,e_2,...,e_N}$, where $e_i = 1$ if
transaction $t_i$ has failed and $e_i = 0$ otherwise; and an
$N\times{}M$ coverage matrix $\mathcal{A}$, where $\A{ij}$ denotes the
coverage of component $c_j$ in transaction $t_i$.  The pair
$(\mathcal{A},e)$ is commonly referred to as
spectrum~\cite{DBLP:journals/stvr/HarroldRSWY00}. Figure~\ref{fig:spectrum-example}
shows an example spectrum.
\begin{wrapfigure}[8]{2}{0.3\textwidth}
  \hspace{-2ex}
  \centering
  \scriptsize
  \begin{tabular}{c|cccc|c}
    $\mathcal{T}$ & $c_1$    & $c_2$    & $\cdots$ & $c_M$    & $e$    \\ \hline
    $t_1$         & $\A{11}$ & $\A{12}$ & $\cdots$ & $\A{1M}$ & $e_1$  \\
    $t_2$         & $\A{21}$ & $\A{22}$ & $\cdots$ & $\A{2M}$ & $e_2$  \\
    \vdots        & \vdots   & \vdots   & $\ddots$ & \vdots   & \vdots \\
    $t_N$         & $\A{N1}$ & $\A{N2}$ & $\cdots$ & $\A{NM}$ & $e_N$  \\
  \end{tabular}
  \caption{An example spectrum.}
  \label{fig:spectrum-example}
\end{wrapfigure}

@@

\section{The \sfl{}+\cs{} combination}
\label{sec:combination}

%% \Mar{Sofia, o pseudocodigo acima assume que ha apenas um teste
%%   falho. Isto precisa ser ajustado. O lithium-slicer funciona por caso
%%   de teste ou por suite?  Por favor, ajuste a descricao acima.  Eh um
%%   loop aninhado ao loop ``for every k'' que o lithium-slicer
%%   implementa (algo como ``for every k and every failing test'')?  Caso
%%   vc. faca slice contra um teste particular, vc. garante (checa saida)
%%   que os demais testes que originalmente falhavam continuam falhando
%%   pelo mesmo motivo? Enfim, isto eh bem basico e precisa ficar claro
%%   de inicio.}

%% \Sof{O lithium-slicer funciona por caso de teste. Cada execução da nossa
%% ferramenta chama o lithium tantas vezes como o número de casos de teste 
%% que falham para cada versão do projecto. Assumindo que o numero de casos de
%% testes a falhar são 5, numa execução da nossa plataforma o lithium é executado
%% 5x para os 5 testes diferentes. No fim, pega no resultado do slicing de cada 
%% teste e actualiza a matrix spectra para calcular o ranking. Eu confiro depois de 
%% executar a nossa ferramenta para uma versão do projecto que os 
%% testes que aparecem na pasta da versão do projecto são os mesmos quando corro 
%% o test do defects4j de novo. Uma precaução que tivemos foi ter a certeza que o
%% oracle que estava a ser usado não sofria com a mudança de máquinas. Portanto,
%% antes de correr as experiências eu corri o defects4j para obter as mensagens
%% esperadas de novo para serem usadas como o oracle esperado. Estas são as verificações
%% que faço. Posso tentar substituir as classes minimizadas nos projectos e ver se
%% realmente a mensagem de erro continua a ser a mesma - coisa que não fiz. Relativamente,
%% ao pseudocode eu diria que é for every $k$ and every failing test.}

To illustrate the idea behind the \sfl{}+\cs{} combination, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

@@

In the following, we illustrate the workflow of the \sfl{}+\cs{}
combination for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the \sfl{}+\cs{} combination consists of four steps:
\begin{enumerate}
  \itemsep0em 
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious source files, according to $R$;
  \item\label{step:compute-slice} Compute slice for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables identification of cells in the spectra
whose values can be set to zero, \ie{}, the components marked with 0
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one can observe that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$. Therefore,
suspiciosness of those components decrease. Similar argument applies
to other fault predictors. In the example from
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

It is possible that a slice that discards the faulty component still
produces the expected message checked by the oracle. This can happen,
for example, if the oracle is too
general. Section~\ref{sec:oracleheuristics} elaborates the heuristics
we used to mitigate this fundamental limitation of Critical Slicing.

%% \vspace{3mm}
%% \begin{myframe} \label{box:1}
%% \textbf{java.lang.NullPointerException}, \\
%% at org.jfree.data.general.junit.DatasetUtilitiesTests.\\
%% testBug2849731$\_$3(DatasetUtilitiesTests.java:1299), \\
%% ...
%% \end{myframe}

@@

The proof is based on the argument aforementioned that irrelevant
components $j$ have their ranks reduced as $\N{11}$ decreases and
$\N{01}$ increases. If those irrelevant components appear at positions
above the faulty component, it is possible that the faulty component
becomes more suspicious relative to $j$, \ie{}, the ranking of the
faulty component increases. If those components appear at positions
below the faulty components, the ranking of the faulty components is
unaffected.

\Mar{parei aqui}
